---
title: "classification"
author: "Gert Sterenborg and Job de Pater"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  knitrBootstrap::bootstrap_document:
    title: "Advanced Raster Analysis"
    theme: cosmo
    menu: FALSE
---

# Visualization of the relationship 
Here some plots are given to visualize the relation between the Landsat bands and the VCF tree cover.

```{r, echo=FALSE, fig.align='center'}
library(png)
library(grid)
img <- readPNG("figs/pairs.png")
grid.raster(img)
```

# Linear model

Output of the linear models is as follows:

```{r, echo=FALSE}
library(pander)
load("out/linMod.rda")
pander(out)
```

Based on the coefficient of variation (R2), the forest cover is best predicted by band 7. 

# Predicted vs original tree cover 

The predicted VCF is plotted versus the original VCF data.

```{r, echo=FALSE, fig.align='center'}
library(png)
library(grid)
img <- readPNG("figs/predictedMeasured.png")
grid.raster(img)
```


# Root mean square error

The root mean square error turned out to be 10.7. The root mean square error was 12.0 for the subclas cropland, 6.7 for forest and 21.7 for the wetland. 


